Making Soup: Preparing and Validating Molecular Simulations of the Bacterial Cytoplasm

### 2019-09-22 paper/virtual_cytoplasm_v2.tex

Under crowded conditions, molecules are constrained to a smaller volume due to collisions with the other components of the crowded environment. This extent of this effect is evident when we compare the translational diffusion constant of each component in the cytoplasm model, $D_{cytoplasm}$, and in a dilute system, $D_{dilute}$ (Figure ~\ref{fig:translational_diffusion}A). The ration of these quantities is independent of the protein size and is always close to 0.13 (Figure ~\ref{fig:translational_diffusion}B). However, the effect of crowding over the translation diffusion of tRNA is two times higher, indicating that its movement is specially constrained in the crowded environment.

>>>>

Under crowded conditions, molecules are constrained to a smaller volume due to collisions with the other components of the crowded environment. This extent of this effect is evident when we compare the translational diffusion constant of each component in the cytoplasm model, $D_{cyto}$, and in a dilute system, $D_{dil}$ (Figure ~\ref{fig:translational_diffusion}A). The ration of these quantities is independent of the protein size and is always close to 0.13 (Figure ~\ref{fig:translational_diffusion}B). However, the effect of crowding over the translation diffusion of tRNA is two times higher, indicating that its movement is specially constrained in the crowded environment.
